---
title: 'Task 14: Data to answer questions'
author: "Chloe Huang"
date: "6/30/2021"
output: 
  html_document: 
    keep_md: TRUE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_libraries, include=FALSE}

#install.packages("tidyverse") 
library(tidyverse)
library(ggforce)
library(downloader)
```
## Q & A

1. What is the percentage of education rate over the past 100 years?
2. What countries have the most education rate and lowest education rate?
3. What is the education rate for different race?
4. What is the education rate between different genders?
5. Which country has the biggest gap for enrollment rate and graduation rate?
6. what is the relationship between education and finance? 


## Data Sources

[1](https://ourworldindata.org/global-education)
[2](https://datacatalog.worldbank.org/dataset/education-statistics)
[3](https://data.worldbank.org/topic/4)
[4](https://www.oecd-ilibrary.org/education/data/education-at-a-glance_eag-data-en)

## Read the data and visualizes the data

```{r}
data0 <- read_csv("~/Desktop/EAG_FIN_RATIO.csv")
data1 <- read_csv("~/Desktop/Edstats_csv/EdStatsData.csv")

data2 <- read_csv("~/Desktop/Edstats_csv/EdStatsCountry.csv")
```

```{r}

ed_data <- data0 %>%
  select(c(Country, ISC11, COUNTERPART_SECTOR, Year))

ed_data2 <- data1 %>%
  pivot_longer(cols = starts_with("1970"), names_to = "Year")

ed_data3 <- data2 %>%
  select(c(Region,'Income Group', ))

  
```

## Summarize 

source 1 : This website provides some overview of the literate and illiterate for the global education. There are different ways to visualized the data by using different graph. 
source 2 & 3: The advantage from this website is that I can get all the data files I need from it. 
source 4: This website can help me to collect the data as well. 

