---
title: 'Case Study 3: Give Your Visualization Wings to Fly'
author: "Chloe Huang"
date: "6/7/2021"
output: 
  html_document:
    keep_md: True
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nycflights13)
library(tidyverse)
```



# Question 1
If I am leaving before noon, which two airlines do you recommend at each airport (JFK, LGA, EWR) that will have the lowest delay time at the 75th percentile?

We can see that based on this diagram, the airlines with the lowest delay time for each airport are listed below
EWR airport: Endeavor Air (EV) and US Airways (UA) 
JFK airport: Delta Airlines (DL) and Hawaiian Airlines (HA)
LGU airport: US Airways (UA) and Mesa Airlines (YV)

```{r}
lowdelaytime <- flights %>%
  filter(dep_time < 1200)

#view(lowdelaytime)

ggplot(lowdelaytime, aes(x=carrier, y=dep_delay, fill = "red")) +
  theme_bw() +
  facet_wrap(. ~origin, nrow = 3) +
  geom_boxplot(outlier.shape = NA) +
  ylim(-10,7) +
  labs(x = 'Airline', y = 'Departure Delay Time', title = 'Delaytime by Airline') +
  theme(plot.title = element_text(hjust = 0.5))
  

```

## Question 2
Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?

Based on the delay probability results, JFK has the lowest probability of arrival delayed flights, thus, it's the best option to minimize the chances of late arrival. 

```{r}

# #get all the delta flights for each airport
# flight <- flights %>% filter(carrier == 'DL')
# table(flight$origin)
# 
# #get all the arrive delay flights 
# flight <- flights %>% filter(carrier == 'DL' & arr_delay > 0)
# table(flight$origin)
# 
# #calculate the probability of the delay flights
# deltaflight <- flight %>%
#   group_by(origin) %>%
#   mutate(
#     probability = case_when(
#       origin == 'EWR' ~round(((1725/4342)*100),3),
#       origin == 'JFK' ~round(((6353/20701)*100),3),
#       origin == 'LGA' ~round(((8335/23067)*100),3)
#     )
#   ) %>%
#   distinct(origin, probability)
# 
# 
# table(deltaflight$origin)
# 
# ggplot(deltaflight, aes(x = origin, y = probability)) +
#   geom_bar(stat="identity",fill="skyblue", width = 0.5) +
#   labs(title = 'Probability of Delta delay arrived flights', x = 'Airport', y = 'Probability')


#This version uses summarise instead of mutate
flights %>%
  filter(carrier == "DL") %>%
  filter(!is.na(arr_delay)) %>%
  group_by(origin) %>%
  summarise(total_flights = n(),
            num_delay = sum(arr_delay>0),
            probability = num_delay/total_flights)

ggplot(deltaflight, aes(x = origin, y = probability)) +
  geom_bar(stat="identity",fill="skyblue", width = 0.5) +
  labs(title = 'Probability of Delta delay arrived flights', x = 'Airport', y = 'Probability')

  
```


<!-- ## Question 3 -->
<!-- Which destination airport is the worst airport for arrival time? (you decide on the metric for "worst") -->


